\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-07 paper.qmd
Updated Figure 14 title

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the tSNE layout (a), and three views of the fit in projections from $9\\text{-}D$ (b, c, d), for the PBMC3k data ($a_1 = 0.099$, $b = 221 \\  (13, \ 17)$, $m = 92$, benchmark value to remove large edges is $0.1$). The three well-separated clusters with small separations observed in the \\gD{} layout of tSNE (@fig-NLDR-variety (e)) is also visible when visualizing the model overlaid on the data space in $9\\text{-}D$. Furthermore, there are some non-linear clusters. The model shows densed points within clusters in $9\\text{-}D$ space, which is an additional patterns not visible in the \\gD{} representation (@fig-NLDR-variety (e)). The full video is available at <https://youtu.be/5Y1hE4i7N2k>."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 10

>>>>

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the layouts, and two views of the fit in projections from $9\\text{-}D$, for the PBMC3k data. The \\gD{} model shows three well-separated clusters with large gaps in a1 ($a_1 = 0.05$, $b = 676 \\  (26, \ 26)$, $m = 92$, benchmark value to remove large edges is $0.08$), while a2 ($a_1 = 0.10$, $b = 195 \\  (13, \ 15)$, $m = 90$, benchmark value to remove large edges is $0.166$) shows small separation between the clusters. Because of the small separation, the three clusters are connected in \\gD{} and appear as long edges in $9\\text{-}D$. The full video for the model for layout a is available at <https://youtu.be/5Y1hE4i7N2k>. The full video for the model for layout c is available at <https://youtu.be/5Y1hE4i7N2k>."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-height: 80%

### 2024-09-07 paper.tex
Updated Figure 14 title

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-model-pbmc-author-proj-1.pdf}

@@

\caption{\label{fig-model-pbmc-author-proj}Model in \gD{}, on the tSNE
layout (a), and three views of the fit in projections from
\(9\text{-}D\) (b, c, d), for the PBMC3k data (\(a_1 = 0.099\),
\(b = 221 \  (13,  17)\), \(m = 92\), benchmark value to remove large
edges is \(0.1\)). The three well-separated clusters with small
separations observed in the \gD{} layout of tSNE
(Figure~\ref{fig-NLDR-variety} (e)) is also visible when visualizing the
model overlaid on the data space in \(9\text{-}D\). Furthermore, there
are some non-linear clusters. The model shows densed points within
clusters in \(9\text{-}D\) space, which is an additional patterns not
visible in the \gD{} representation (Figure~\ref{fig-NLDR-variety} (e)).
The full video is available at \url{https://youtu.be/5Y1hE4i7N2k}.}

>>>>

\includegraphics[width=1\textwidth,height=0.8\textheight]{paper_files/figure-pdf/fig-model-pbmc-author-proj-1.pdf}

@@

\caption{\label{fig-model-pbmc-author-proj}Model in \gD{}, on the
layouts, and two views of the fit in projections from \(9\text{-}D\),
for the PBMC3k data. The \gD{} model shows three well-separated clusters
with large gaps in a1 (\(a_1 = 0.05\), \(b = 676 \  (26,  26)\),
\(m = 92\), benchmark value to remove large edges is \(0.08\)), while a2
(\(a_1 = 0.10\), \(b = 195 \  (13,  15)\), \(m = 90\), benchmark value
to remove large edges is \(0.166\)) shows small separation between the
clusters. Because of the small separation, the three clusters are
connected in \gD{} and appear as long edges in \(9\text{-}D\). The full
video for the model for layout a is available at
\url{https://youtu.be/5Y1hE4i7N2k}. The full video for the model for
layout c is available at \url{https://youtu.be/5Y1hE4i7N2k}.}
